\documentclass[11pt]{report}

\usepackage{geometry}
\geometry{left=1.25in, right=1.25in}

\usepackage{graphicx}
\graphicspath{ {./media/} }

\makeatletter
\renewcommand{\maketitle}{
        {\Large \bf \@title}
        \vspace{0.75em}

        {\normalsize \@author}
        \vspace{0.25em}

        {\normalsize \@date}
        \vspace{1em}

}
\makeatother

\begin{document}
\title{Self-Assembly Exercises}
\date{\today}
\author{Makise Kurisu}
\maketitle

\textbf{Exercise 0.}
If you are allowed to use exactly five different glue labels and three different glue strengths (0,
1 or 2), then how many unique tile types could you make? (Note that there is considered to be a
single glue of strength 0 called the null glue.)

There are 11 different glue label and glue strength combinations (5 for each glue label of
strength 1, 5 for each glue label of strength 2, and an additional 1 for the null glue). Each of the
four sides of a tile can hold any of the 11 different glue labels. Therefore, there are a total of
$11^4 = 14641$ unique tile types you can make.

\textbf{Exercise 1.}
Make a base-3 counter. Successive rows should represent successive numbers, represented in base-3.
Your tile set for this problem should produce the same (infinite) structure each time, no matter
what order individual tiles are added. 

\textbf{Exercise 2.} 
Make a base-2 counter with the property that each row contains only as many tiles as it needs for
the base-2  representation of whatever number it represents. So, for example, the row that
represents the number five should only have three tiles in it: one for each bit in the binary
representation of 5 (101). If your counter gets "thicker-to-the-left", then the least significant
bit should be represented by the tile in the rightmost column of tiles for the counter. Your tile
set for this problem should produce the same (infinite) structure each time, no matter what order
individual tiles are added. Your tile set must work at temperature 2 for this problem.

\textbf{Exercise 3.}
Make an assembly which grows to 100 rows tall and then stops growing. Each row must represent a
positive number in base-2. Each row can either be finite (like \#2) or have infinitely many leading
0's (like the example base-2 counter). In either case, the final assembly must contain exactly 100
rows of tiles. Your tile set for this problem should produce the same structure each time, no matter
what order individual tiles are added. Your tile set must work at temperature 2 for this problem.
Hint: not every row needs to represent a different value! This may seem tricky at first! 

\end{document}
